SPDE approach notes

### 2022-11-10 src/0_explore_inla-spde/inla-spde.Rmd
INLA-SPDE notes to HTML
Update explore_inla-spde

---
title: "SPDE approach notes"
author: "Adam Howes"
output: pdf_document
bibliography: citations.bib
---

## List of possible sources

@@

## Background

@@

## @miller2020understanding explanation

@@

### Connection to basis-penalty smoothing

@@

## A short introduction on how to fit a SPDE model with INLA (Krainski and Rue)

@@

## @krainski2018advanced notes

### First result

@@

### Second result

@@

### Toy example

@@

## Bibliography {-}

>>>>

---
title: "SPDE approach notes"
author:
- name: Adam Howes
output:
  html_document:
    toc: yes
    toc_float: yes
    toc_collapsed: yes
    df_print: paged
    code_folding: show
    theme: lumen
bibliography: citations.bib
abstract: |
  **Background** To write.
---

# Resources

@@

# Background

@@

# @miller2020understanding explanation

@@

## Connection to basis-penalty smoothing

@@

# A short introduction on how to fit a SPDE model with INLA (Krainski and Rue)

@@

# @krainski2018advanced notes

## First result

@@

## Second result

@@

## Toy example

@@

# Original computing environment

```{r}
sessionInfo()
```

# Bibliography {-}
